%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Chunghwa Telecom Co., Ltd.} % Organization
    {Taipei, Taiwan} % Location
    {Sept. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed REST APIs integrated with Google third-party APIs to resell Google Workspace. [Go, Google APIs]}
      \item {Working on processing telemetry data and sending events to Azure Event Hubs. [Java (Spring boot), Azure, Multithreading]}
      \item {Working on developing a containerized backend service including REST API and DB schema design to manage devices, cables and patch panels. [Python (FastAPI), MySQL, Docker]}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Shop123 Network Technology Inc.} % Organization
    {Taipei, Taiwan} % Location
    {Jun. 2018 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mainly responsible for developing backend services for a platform which allows users to build an online store with ease.}
	\item {Implemented factory method pattern for creating widgets which rendering inconcrete view objects. [HTML, JavaScript, Bootstrap]}
	\item {Designed database schema and REST APIs for content management module. [PHP (yii), MariaDB]}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {SunFun Info Co., Ltd.} % Organization
    {Taipei, Taiwan} % Location
    {Jul. 2016 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a matchmaking web application and implemented Gale–Shapley algorithm to resolve Stable Marriage Problem.}
        \item {Implemented the online payment service with E.SUN BANK cash management service (e-Collection) to receive payments.}
	\item {Integrated Google Calendar, URL shorten APIs for activity sign-up and Facebook Graph API for member registration.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
