%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Contributor} % Job title
    {Apache Software Foundation, YuniKorn} % Organization
    {} % Location
    {Dec. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {YuniKorn is a standalone resource scheduler for K8s, that empowers to run large-scale batch jobs and services on a multi-tenancy K8s cluster. I added e2e test for admission controller to increase test coverage. Now I am working on some issues about improving the stability for YuniKorn scheduler.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Committer} % Job title
    {Apache Software Foundation, Submarine} % Organization
    {} % Location
    {Oct. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enabled Submarine to run distributed MXNet jobs on Hadoop YARN via an open-source project called TonY. [Java, Hadoop]}
	\item {Integrated Jupyter notebook into Submarine on K8s and enabled users to manage their own notebook instances via REST APIs. [Jersey, Jupyter Notebook, Helm, K8s, MySQL]}
	\item {Deployed Traefik ingress controller on K8s cluster to manage external access to the services in Submarine. [K8s, Traefik, Helm]}
	\item {Analyzed the demand of data scientists on Machine Learning pipelines. [Airflow, Argo workflow, MinIO]}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
